Supplemental Materials, Methods and Results

### 2021-05-05 supp.Rmd
Updated functions. Added data for local adpation plots.

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, pander, kableExtra, flextable, jpeg, clubSandwich)

p_value <- function(x){
  if(x <= 0.0001) {tmp = "< 0.0001"}
  if(x <= 0.001 & x >= 0.0001) {tmp ="< 0.001"}
  if(x <= 0.01 & x >= 0.001) {tmp ="< 0.01"}
  if(x >= 0.01) {tmp = round(x, digits =2)}
  return(tmp)
}
```

@@

### Changes in visual signals across body regions show similar patterns
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across these different body regions because we were interested only in whether visual signals were different in Kenya and Hawaii overall. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figure \@ref(fig:FigS1) and Table \@ref(tab:tableS1)).

@@

```{r FigS3, fig.width = 14.33333, fig.height = 11.00000, fig.cap = "Local adaptation. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

@@

```
# References

>>>>

```{r getlibrary, echo = FALSE, results = "hide"}
# load libraries
devtools::install_github("karthik/wesanderson")
pacman::p_load(lme4, lmerTest, ggplot2, lsmeans, emmeans, multcomp, dplyr, wesanderson, patchwork, latex2exp, png, cowplot, magick, jpeg, clubSandwich)
source("./R/func.R")
```

@@

### Changes in visual signals across body regions show similar patterns
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals were different in Kenya and Hawaii overall. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figure \@ref(fig:FigS1) and Table \@ref(tab:tableS1), \@ref(tab:tableS2)).

@@

```{r FigS2.1, fig.width = 14.33333, fig.height = 11.00000, fig.cap = "Local adaptation. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

```{r FigS2, fig.width = 14.33333, fig.height = 11.00000, fig.cap = "Local adaptation. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}
# Courship data

CourtshipBgrd <- read.table("./data/Courtship_5.csv", 
                        header=TRUE, sep=",", dec=".", strip.white=TRUE)

CourtshipBgrd <- CourtshipBgrd %>% 
                filter(!BodyRegion == "botflank") %>% 
                mutate(Background_pop = ifelse(Background2 == "own", Population, if_else(Background2 == "other" & Population == "Hawaii", "Kenya", "Hawaii"))) %>% 
                as.data.frame() #exclude bottom flank.
CourtshipBgrd$BodyRegion <- factor(CourtshipBgrd$BodyRegion)

# Display data
DisplayBgrd <- read.table("./data/Display_5.csv", 
                        header=TRUE, sep=",", dec=".", strip.white=TRUE)

DisplayBgrd <- DisplayBgrd %>% 
                filter(!BodyRegion == "botflank") %>% 
                mutate(Background_pop = ifelse(Background2 == "own", Population, if_else(Background2 == "other" & Population == "Hawaii", "Kenya", "Hawaii"))) %>% 
                as.data.frame() #exclude bottom flank.
DisplayBgrd$BodyRegion <- factor(DisplayBgrd$BodyRegion) #updates levels for the variable BodyRegion

@@

# References
